Quantifying the home ground advantage with `hyper2` and `hyper3` objects

### 2025-02-14 inst/home_advantage.Rmd
home_draw_away3()

<font size="1"> (takes about fifteen minutes to run without cache)
</font>

@@

(from here on we ignore draws and consider only won games)

@@

>>>>

<font size="1"> most of the time is taken calculating the contour
graph right at the end; takes about an hour to run without cache for
n=10 </font>

@@

(We will ignore draws for the moment, and consider only won games)

@@

# Bring back draws

```{r, bbdlambdaD,cache=TRUE}
aT
home_draw_away3(aT,lambda=1.888,D=0.3)
f <- function(v){
    H <- home_draw_away3(aT, lambda = v[1], D=v[2])
    maxp(H,give=1)$`Log-likelihood`
}
n <- 20
lambda_try <- seq(from=1.6,to=4,len=n)
D_try <- seq(from=0.3,to=1,len=n)
V <- as.matrix(expand.grid(lambda_try,D_try))
LL <- apply(V,1,f)
```

```{r plotLL}
LL <- matrix(LL,n,n) - max(LL)
LL <- pmax(LL,-10)
contour(lambda_try, D_try, LL,xlab="lambda",ylab="D")
```
